Relational Presentations Using Semantic Closeness\\Spatial Narrative for Mathematical Content

### 2015-05-29 Paper.tex
coppred
more

\begin{wrapfigure}{r}{0.36\textwidth}
\vspace{-2em}\centering
  \fbox{
    \includegraphics[width=0.36 \textwidth]{assets/final/straightMountain}}    \vspace{-20pt}
    \caption{Straight Learning Path}\label{fig:straight}
    \vspace{5pt}  
      \fbox{\includegraphics[width=0.37 \textwidth]{assets/final/curvyMountain}}
      \vspace{-20pt}
      \caption{Winding Learning Path}\label{fig:curvy}
      \vspace{-10pt}
\end{wrapfigure}

Learning new things is a bit like hiking up a mountain. If you have ever gone hiking, you know that it is hard to hike up a steep mountain directly as shown in \autoref{fig:straight}. Some people do it but most people will rather hike up as shown in \autoref{fig:curvy}. Both paths lead to the goal though. Within Mathematics classes, there is normally only one straight path and this has not changed in decades. With the advancement of technology, we are however able to change the way presentations and their narratives work. We can make it possible to link content that logically belongs together, in other words, content that is semantically close. Through the linking of content it becomes possible for a presenter to seamlessly lead an audience, not along a predetermined straight path, but rather along the path that allows the audience to take small detours and ultimately make the most out of the presentation.

\begin{wrapfigure}{l}{0.45\textwidth}\centering\vspace{-2em}
  \fbox{\includegraphics[width=0.43 \textwidth]{assets/final/slide_theorem}}\vspace{-.5em}
  \caption{Theorem Slide}\label{fig:slideP}
  \vspace{-15pt}
\end{wrapfigure}

Let us dive into a contrived story that will guide us throughout this research: Annie, a young student learning mathematics, is watching her teacher give a presentation on how to use the Pythagorean theorem (see \autoref{fig:slideP}). She is then given a triangle with sides a = 3 cm and b = 4 cm. Now she wants to use the theorem to calculate the length of side c. Annie already knows how to calculate the square of a number and thus calculates that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right triangle is. Her teacher tells her that the question was a trick question and that the answer is wrong because the triangle she calculated this for is not a right triangle. Now Annie has to try to find out what a right triangle is.

@@

After asking the user for the location and names of the folders we want to work on, \sys can parse the provided \stex files in a recursive fashion to retrieve the slide order. It does this by starting with a given top level file which includes other files via \textit{mhinputref}s.

@@

\begin{center}
\textit{"My sister went to the circus the other day; \underline{she} said \underline{it} was brilliant."}
\end{center}

>>>>

\begin{wrapfigure}{r}{0.36\textwidth}
\vspace{-2em}\centering
  \fbox{
    \includegraphics[width=0.36 \textwidth]{assets/final/straightMountain}}    \vspace{-1.8em}
    \caption{Straight Learning Path}\label{fig:straight}
    \vspace{5pt}  
      \fbox{\includegraphics[width=0.37 \textwidth]{assets/final/curvyMountain}}
      \vspace{-1.8em}
      \caption{Winding Learning Path}\label{fig:curvy}
      \vspace{-2em}
\end{wrapfigure}

Learning new things is a bit like hiking up a mountain. If you have ever gone hiking, you
know that it is hard to hike up a steep mountain directly as shown in
\autoref{fig:straight}. Some people do it but most people will rather hike up as shown in
\autoref{fig:curvy}. Both paths lead to the goal though. Within Mathematics classes, there
is normally only one straight path and this has not changed in decades. With the
advancement of technology, we are however able to change the way presentations and their
narratives work. We can make it possible to link content that logically belongs together,
in other words, content that is semantically close. Through the linking of content it
becomes possible for a presenter to seamlessly lead an audience, not along a predetermined
straight path, but rather along the path that allows the audience to take small detours
and ultimately make the most out of the presentation.\ednote{This intro does not work for
  math. Math instruction is mostly done via blackboard, and teachers can flexibly take any
  path they want with that in response to student understanding (or lack, ... ). Maybe we
  can turn this around: math uses blackboard, because it is flexible. Presentations are
  too inflexible for math, let's make them better.}

\begin{wrapfigure}{l}{0.45\textwidth}\centering\vspace{-2em}
  \fbox{\includegraphics[width=0.43 \textwidth]{assets/final/slide_theorem_cropped}}\vspace{-.5em}
  \caption{Theorem Slide}\label{fig:slideP}
  \vspace{-15pt}
\end{wrapfigure}

Let us use a contrived story to guide our intuitions: Annie, a young student learning
mathematics, is watching her teacher give a slide-based presentation on how to use the
Pythagorean theorem (see \autoref{fig:slideP}). She is then given a triangle with sides
$a = 3 cm$ and $b = 4 cm$. Now she wants to use the theorem to calculate the length of
side $c$. Annie already knows how to calculate the square of a number and thus calculates
that $c^2 = 25 \implies c = 5$. However Annie made a mistake and did not know what a right
triangle is. Her teacher tells her that the question was a trick question and that the
answer is wrong because the triangle she calculated this for is not a right triangle. Now
Annie has to try to find out what a right triangle is.

@@

After asking the user for the location and names of the folders we want to work on, \sys
can parse the provided \stex files in a recursive fashion to retrieve the slide order. It
does this by starting with a given top level file which includes other files via
\texttt{\textbackslash mhinputref} macros.

@@

\begin{quote}\em
  My sister went to the circus the other day; \underline{she} said \underline{it} was
  brilliant.
\end{quote}
